Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-04-23 doc/PRF2022/PRF_main.tex
updated derivation

Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:stokes}
into smooth portion $w_i$ and singular portion $u_i$. That is, $u = w_i + u_i$.
Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as

\begin{align}
\label{eq:free_energy2}
  E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
\end{align}
%%%
Follow the divergence theorem on the last term in the equation above and denote $g_i(x)$ as the boundary data on $\Gamma_i$, we obtain
\begin{align}
\label{eq:free_energy3}
  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g \frac{\partial w_i}{\partial \nnu} \,\dif s 
  + \int_{U_i}\nabla g_i \nabla u_i + g_i (u_i+\frac12\sigma) \,\dif \xx\right)\\
  &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu} 
 + u_i \frac{\partial g_i}{\partial \nnu} \,\dif s - \int_{U_i}\Delta g_i u_i - g_i (u_i+\frac12\sigma) \,\dif \xx\right) \\
 &= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g \frac{\partial w_i}{\partial \nnu}+ (u_i+\frac12\sigma)  \frac{\partial g_i}{\partial \nnu}\,\dif s, \quad \xx\in\Gamma_i.
\end{align}
%
$\sigma$ satisfies the second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  g(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
    \dif s_\yy, \quad \xx \in \bd\Omega,
\end{equation}

>>>>

Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:SL}
into smooth portion $w_i$ and singular portion $u_i$. That is, 
\begin{equation}
w_i({\bf x}) = u({\bf x}) - u_i = u({\bf x}) - \int_{\Gamma_i }\left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma_i(\yy) \,
    \dif s_\yy \quad \xx \in \Gamma_i.
\end{equation}
Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as

\begin{align}
\label{eq:free_energy2}
  E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} u \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
\end{align}
%%%
Follow the divergence theorem on the last term in the equation above and denote $g_i(x)$ as the boundary data on $\Gamma_i$, we obtain
\begin{align}
\label{eq:free_energy3}
  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} \left( \nabla u \cdot\nabla u_i + u\Delta u_i\right) \,\dif \xx\right)\\
%
&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx
+\int_{\Gamma_i}\left(u_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu} \,\dif s     
- \int_{\mathbb{R}^n\setminus \overline{U}_i} u_i\Delta u\,\dif \xx \right)\\
&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} + 
\left(g_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu}   \,\dif s \right).
\end{align}

%  &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu} 
% +  \left(u_i+\frac12\sigma\right)  \frac{\partial g_i}{\partial \nnu} \,\dif s - \int_{\mathbb{R}^n\setminus \overline{U}_i}\Delta g_i  \left(u_i+\frac12\sigma\right)  - g_i \left(u_i+\frac12\sigma\right) \,\dif \xx\right) \\
% &= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu}+ \left(u_i+\frac12\sigma\right)  \frac{\partial g_i}{\partial \nnu}\,\dif s, \quad \xx\in\Gamma_i.

%%
%$\sigma$ satisfies the second-kind integral equation
%\begin{equation}
%\label{eq:screenedSKIE}
%  g(\xx) = \frac{1}{2}\sigma(\xx) + 
%    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
%    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
%    \dif s_\yy, \quad \xx \in \bd\Omega,
%\end{equation}
